What We Eval in the Shadows

### 2021-08-10 paper/main.tex
stuff

\documentclass[screen,acmsmall]{acmart}
%\settopmatter{printfolios=false,printccs=false,printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

\bibliographystyle{ACM-Reference-Format}
\citestyle{acmauthoryear}   %% For author/year citations
\usepackage{listings,hyperref,multirow,paralist,xspace,url,wrapfig,tikz}
\usetikzlibrary{positioning,automata,fit,shapes.geometric,backgrounds,calc}
\usepackage{tabularx}
\input{macro}
\newcommand{\mypara}[1]{\medskip\noindent\emph{#1}\xspace}
\newcommand{\NOTE}[1]{{\it Note: #1}\xspace}
\newcommand{\authorcomment}[3]{\xspace\textcolor{#1}{{\bf #2} #3}\xspace}
\newcommand{\todo}[1]{\authorcomment{red}{TODO}{#1}}
\newcommand{\code}[1]{\lstinline |#1|\xspace}
%\renewcommand{\c}[1]{\lstinline |#1|\xspace}
% cf. https://tex.stackexchange.com/a/144640
\makeatletter\let\expandableinput\@@input\makeatother

%% https://www.davehofmann.de/defining-custom-language-templates-for-latex-listings/
% Define Language
\lstdefinelanguage{smalleR} {
  % list of keywords
  morekeywords={
    for,
    if,
    else,
    function
  },
  sensitive=true, % keywords are not case-sensitive
  morecomment=[l]{\#}, % l is for line comment
  morestring=[b]{"} % defines that strings are enclosed in double quotes
}

\lstset{
  language={smalleR},
  columns=flexible,
  captionpos=b,
  frame=single,
  framerule=0pt,
  framexleftmargin=1mm,
  framexrightmargin=1mm,
  tabsize=2,
  belowskip=0pt,
  basicstyle=\small\ttfamily,
  backgroundcolor=\color{LightGray},
  emphstyle=\sffamily,
  keywordstyle=\bfseries,
  commentstyle=\color{Gray}\em,
  stringstyle=\color{Gray},
  alsoletter={., _, $},
  breaklines=true
}

@@

\maketitle
\renewcommand{\shortauthors}{A. Goel, P. Donat-Bouillud, F. Křikava, C. Kirsch and J. Vitek}

@@

\vspace{2mm}\noindent\emph{Trouble in Paradise.} Reflective facilities hinder
most attempts to reason about or apply meaning-preserving transformations to the
code using them. In practice, \eval causes static analysis techniques to lose so
much precision as to become pointless. For compilers, anything but the most
trivial, local optimizations are unsound after the use of \eval. Furthermore,
the addition of arbitrary code --- code that could have been obtained from a
network connection --- as a program is running is a security vulnerability
waiting to happen. To illustrate these challenges, consider the interaction of a
static analysis tool with a dynamic language. An abstract interpretation-based
program analyzer computes an over-approximation of the set of possible behaviors
exhibited by the program under study~\cite{cc77}. A reflective facility may have
\emph{any} behavior that can be expressed in the target language, \ie any legal
sequence of instructions can replace \eval. As dynamic languages tend to be
permissive, the analysis has to, for example, assume that many (or all)
functions in scope may have been redefined, \eg that \texttt{`+`} now opens a
network connection or something equally surprising. A single occurrence of \eval
causes the static analyzer to lose all information about the program state and
meaning of identifiers. This loss of precision can sometimes be mitigated by
analyzing the string argument~\cite{moller03} to bound its possible behavior,
but when the string comes from outside the program, not much can be done. A
frustrated group of researchers argued giving up on soundness and, instead,
under-approximating dynamic features (soundiness)~\cite{soundy}. In their words,
``a practical analysis, therefore, may pretend that \eval does nothing unless it
can precisely resolve its string argument at compile time.'' Alas, assuming that
\eval does not have side-effects or that side-effects will not affect the
results of the analysis may be unduly optimistic.

\vspace{2mm}\noindent\emph{Is Past Prologue?} Previous work investigated how
\eval is used in web programming, specifically in websites that use
JavaScript~\cite{pldi10a}. In 2010, 17 of the largest websites used the feature.
In 2011, 82\% of the 10,000 most accessed sites used \eval~\cite{ecoop11}. Yet,
the strings passed to \eval, and their behaviors, when executed, are far from
random; it was shown that when one can observe several calls to \eval, the
``shape'' of future calls can be predicted with 97\% accuracy~\cite{oopsla12b}.
Overall, practical usage suggested that most reflective calls were relatively
harmless. While this backs up the soundiness squad's approach, does it
generalize to other application domains than web programming and to other
languages?

\vspace{2mm}\noindent\emph{The Here and Now.} In this study, we investigate the
usage of \eval in programs written in the R programming language. R is a language
designed by statisticians for applications in data science~\cite{r,R96}. What
makes looking at R after JavaScript interesting is that, while both languages
are dynamic, they are quite different. While one can program in an
object-oriented style in R like in JavaScript, R is primarily a lazy, untyped,
functional language. JavaScript was designed to run untrusted code in a browser,
while R is used for statistical computing on desktops. JavaScript is a general-purpose language used by a vast community of programmers, while R is used for
scientific computing by data scientists and domain experts with, often, limited
programming experience. One can distinguish between library implementers,
developers with some programming experience and a working knowledge of R, and
end users, who are typically not expert programmers and often have only a
cursory knowledge of the language.\footnote{Consider that R is lazy like
Haskell. We informally surveyed end users and did not find a single user aware
of this fact. Library developers, on the other hand, know and program
defensively around laziness.} Thus, our goal is to highlight the differences in
usage between JavaScript and R and try to explain those differences in terms of
language features, application domain and programmer experience. Hopefully, some
of our observations will generalize to other languages.
Our data and code are open source and publicly
available: \url{https://github.com/PRL-PRG/evalr-experiment}.

\vspace{2mm}\noindent\emph{The What and How.} One significant benefit of
choosing R is that every package in the CRAN repository is curated and comes
with examples of typical usage. This gives us a large codebase that we can
analyze dynamically. To observe \eval, we built a two-level monitoring
infrastructure:\footnote{Our infrastructure is open source and publicly
available and  will be submitted to the artifact evaluation committee. } we can
monitor R programs by instrumentation --- this gives us access to many
user-visible properties of R programs --- but we can also monitor the
inner workings of the R interpreter --- this allows us to capture details not
exposed at the source level. Dynamic analysis is limited; it can only observe
behaviors triggered by the particular inputs passed to a program. Luckily, CRAN
libraries come with many tests and use-cases. The choice of the corpus is crucial.
Our corpus has been constructed to reflect the levels of sophistication of the R
community. We distinguish between \emph{CRAN packages} (\CranPackages curated
packages that pass stringent quality checks and are equipped with tests and
sample data) and \emph{Kaggle scripts} (\KaggleUnique end-user written programs
that perform a particular data analysis task). It is reasonable to expect that
\eval usage differs between these datasets: the libraries represent a lively
ecosystem with new libraries added each day, while end-user code is often thrown
together, run once, and never revisited.

\vspace{2mm}\noindent\emph{Why do we Eval?} The results of our study suggest
that \eval is widely used for the implementation of the language, and in many
libraries. End-user code makes less frequent and less sophisticated use of
\eval. In many ways, \eval in R is as bad as it gets: it's varied, performs
side-effects and reaches to many environments. By large, the motivations for
\eval relate to various forms of language extensions and meta-programming. \Eval
is used where other languages would provide macros. But, the expressive power of
\eval is higher as it can reach arbitrarily far back in the call stack.

%\newpage
\section{Background and Previous work}

@@

\citet{ecoop12} gave a programming language-centric overview of the R language.
They characterized it as a lazy, vectorized, functional language with a rich
complement of dynamic features expressive enough to layer several object systems
on top of the core language. Most data types are sequences of primitive values
constructed by calling the combination function \c{c}. For instance,
\c{c("Ha","bye")} evaluates to a vector of two strings, constants such as \c{42}
are vectors of length one. To enable equational reasoning, values accessible
through multiple aliases are copied when written to. Furthermore, values can be
tagged by attributes; these are key-value pairs. For instance, the attribute
\c{dim}-\c{c(2,2)} can be attached to the value at \c{x} by the call
\c{attr(x,"dim")$\leftarrow$c(2,2)}. In this case, the addition of this
attribute turns \c x into a matrix. The \c{class} attribute gives a 'class', in
the object-oriented sense, to a value. So, \c{class(x)<-"human"} sets the class
of \c{x} to \c{human}; classes are used for method dispatch. Every linguistic
construct is desugared to a function call, even control flow statements,
assignments, and bracketing. All functions can be shadowed or redefined, making
the language at the same time remarkably flexible and exceedingly challenging to
compile statically as vividly detailed by~\citet{dls19}. R uses a relaxed
call-by-need convention for passing arguments to functions. Each argument is a
thunk composed of an expression, its environment, and a slot for the result;
these are called \emph{promises}. To get the value of an argument, the
corresponding promise must be forced. Once forced, the promise's result is cached
for future use.

@@

While a data-to-code facility is available in many languages, some design
choices affect the expressive power of \eval. The key choices are the input
format, the environment in which generated code is evaluated, and the reflective
operations available to that code. Fig.~\ref{comp} summarizes designs.

@@

The input to \eval can be in any format convertible to code. JavaScript allows
arbitrary strings to be used. Both Julia and R are more restrictive as they
require expressions (or abstract syntax trees). Finally, Java is the most
restrictive as its classloader only accepts complete classes in bytecode form.

The choice of the environment of \eval is essential as it determines how much of
a program \eval can observe as well as the reach of potential side-effects
performed by that operation. The most restrictive semantics is that of Java,
where newly loaded code evaluates in the environment defined by the classes
visible from the current classloader. Julia and JavaScript's strict mode limit
\eval to the global environment. Finally, R is the most flexible as any
accessible environment can be selected and passed to \eval.

The last degree of freedom is the expressive power of the code executed by
\eval. The main difference between languages lies in how much of the state of a
program is accessible through reflective operations. Julia, Java and, JavaScript
all allow some form of introspection on the data. R is more flexible as it is
possible to inspect the program's call stack. Thus, any environment in the
program can be inspected and modified.

@@

The \eval function in R takes three parameters: an \c{expression} to evaluate
(\c{e}), an environment where to evaluate (\c{envir}), and an enclosure
(\c{encl}) that is used to look up objects not found in \c{envir}.\footnote{Next to the \eval function R
  offers three other variants:
  \begin{inparaenum}[1.]
    \item \c{evalq} automatically quotes passed expression---a shorthand to
      \c{eval(quote(...))},
    \item \c{eval.parent(e, n)} specifies the evaluating
      environment in terms of number of call frames (\c{n}) to go back---a shorthand
      to \c{eval(e, parent.frame(n))}, and
    \item \c{local} evaluates \c{e} in a fresh
      environment---a shorthand to \c{evalq(e, new.env())}.
  \end{inparaenum} }
%
\begin{lstlisting}
 eval <- function(e, envir = parent.frame(),
                   encl = if(is.list(envir)) parent.frame() else baseenv()) ...
\end{lstlisting}

\noindent The expression passed to \eval can be thought of as an abstract
syntax tree. It can be parsed from a string, created manually or using
reflection:

\vspace*{-2mm}
\begin{figure}[htb]
\begin{minipage}{.49\textwidth}
\begin{lstlisting}[caption={Examples of calls producing expression \c{a+b}}]
  parse(text="a+b")
  quote(a+b)
  call("+", quote(a), quote(b))

@@

\vspace*{-2mm}
\noindent The call to \c{substitute(x)} extracts the unevaluated expression from the
promise \c{x}. The function \c{match.call} returns an expression representing the current call.

@@

\citet{ecoop11} provided the first large-scale study of the runtime behavior of
\eval in JavaScript. They dynamically analyzed a corpus of the 10,000 most
popular websites with an instrumented web browser to gather execution traces.
They show that \eval is pervasive, with 82\% of the most popular websites using
it. The reasons for its use include the desire to load code on demand,
deserialization of JSON data, and lightweight meta-programming to customize web
pages. While many uses were legitimate, just as many were unnecessary and could
be replaced with equivalent and safer code. They categorized inputs to \eval so
as to cover the vast majority of input strings. Restricting themselves to \eval
in which all named variables refer to the global scope, many patterns could be
replaced by more disciplined code~\cite{oopsla12b, moller12}. The work did not
measure code coverage, so the numbers presented are a lower bound on possible
behaviors. Furthermore, JavaScript usage in 2011 is likely different from today,
\eg Node.js was not covered. More details about dynamic analysis of JavaScript
can be found in~\cite{liang}.

@@

\vspace{1mm} 
\noindent The pipeline runs in parallel~\cite{GNUparallel}
orchestrated by a Makefile. Servers have identical environments thanks to a
docker image with all dependencies installed\footnote{The docker image is part
  of the accompanied artifact available at\\
\url{https://github.com/PRL-PRG/evalr-experiment/tree/oopsla21}}.

@@

\begin{wrapfigure}{4}{5.8cm}
  \small
  \vspace*{-2mm}
\centering
  \begin{tabular}{|r@{\,}r@{\,}l@{\,}r|r@{\,}r@{\,}l@{}r|} \hline
\multicolumn{3}{|c}{\#calls} & \#sites &
\multicolumn{3}{c}{\#calls} & \#sites \\\hline
\tt 0 &--& \tt 50    & \packageRunbina & \tt 501 &--& \tt 1000   & \packageRunbine\\
\tt 51 &--& \tt 100  & \packageRunbinb & \tt 1001 &--& \tt 1500  & \packageRunbinf\\
\tt 101 &--& \tt 250 & \packageRunbinc & \tt 1501 &--& \tt 2000  & \packageRunbing\\
\tt 251 &--& \tt 500 & \packageRunbind & \tt 2001 &--& \tt 3000 & \packageRunbinh\\\hline
\end{tabular}

@@

\medskip\noindent\EE{$min(e)=\c{V}$} Expressions that represent values are
frequently passed to \eval -- they occur in 17\% of sites. The majority of
those, \packageValOneNodePercent, are inline constants (integer or double
vectors). The rest trivially evaluate to a value, \eg~\c{1+1}.\footnote{True as
long as base functions such as \c{+} are not redefined. They typically are not,
but this is a limitation of this categorization.} In our corpus,
\packageNbCallSitesUniqueActualValue call sites only ever see a simple value,
such as:
\begin{lstlisting}
 f1 <- eval(paste("A~",paste(paste(names(X[,-1])),collapse="+")))
\end{lstlisting}
where the argument to \eval is a string which \eval simply returns. Of twenty
randomly selected \evals, \packageUsefulValueEvalPercent of them need \eval for
some inputs. Either we are dealing with a value that needs to be constructed
dynamically, or the value is a default case that sometimes is replaced by a more
interesting expression. This form is usually evaluated in few interpreter steps;
in fact, the median is only \packageMinimizedmedianoperationscRnd. The
environment in which they evaluate is mostly irrelevant.

@@

\vspace{1mm}\noindent Table~\ref{tab:provenance} summarizes the expression
provenance in our corpus. This data is obtained by dynamically tainting values
as they are produced by the various sources. Due to technical reasons, there is
some imprecision in the results. In particular, we are not able to classify all
sites. Manual inspection of numerous examples suggests that errors are rare.

>>>>

\documentclass[screen,acmsmall]{acmart}%\settopmatter{printfolios=false,printccs=false,printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

\bibliographystyle{ACM-Reference-Format}
\citestyle{acmauthoryear}   %% For author/year citations
\usepackage{listings,hyperref,multirow,paralist,xspace,url,wrapfig,tikz}
\usetikzlibrary{positioning,automata,fit,shapes.geometric,backgrounds,calc}
\usepackage{tabularx}
\input{macro}
\newcommand{\mypara}[1]{\medskip\noindent\emph{#1}\xspace}
\newcommand{\NOTE}[1]{{\it Note: #1}\xspace}
\newcommand{\authorcomment}[3]{\xspace\textcolor{#1}{{\bf #2} #3}\xspace}
\newcommand{\todo}[1]{\authorcomment{red}{TODO}{#1}}
\newcommand{\code}[1]{\lstinline |#1|\xspace}
%\renewcommand{\c}[1]{\lstinline |#1|\xspace}
% cf. https://tex.stackexchange.com/a/144640
\makeatletter\let\expandableinput\@@input\makeatother
\lstdefinelanguage{smalleR} {
  morekeywords={
    for,
    if,
    else,
    function
  },
  sensitive=true, % keywords are not case-sensitive
  morecomment=[l]{\#}, % l is for line comment
  morestring=[b]{"} % defines that strings are enclosed in double quotes
}
\lstset{
  language={smalleR},
  columns=flexible,
  captionpos=b,
  frame=single,
  framerule=0pt,
%  framexleftmargin=1mm,
%  framexrightmargin=1mm,
  tabsize=2,
  belowskip=0pt,
  basicstyle=\small\ttfamily,
  backgroundcolor=\color{LightGray},
  emphstyle=\sffamily,
  keywordstyle=\bfseries,
  commentstyle=\color{Gray}\em,
  stringstyle=\color{Gray},
  alsoletter={., _, $},
  breaklines=true
}

@@

\maketitle
\renewcommand{\shortauthors}{Goel et al.}
\renewcommand{\shorttitle}{What We Eval in the Shadows}

@@

\paragraph{Trouble in Paradise.} Reflective facilities hinder
most attempts to reason about or apply meaning-preserving transformations to the
code using them. In practice, \eval causes static analysis techniques to lose so
much precision as to become pointless. For compilers, anything but the most
trivial, local optimizations are unsound after use of \eval. Furthermore, the
addition of arbitrary code --- code that could have been obtained from a network
connection --- as a program is running is a security vulnerability waiting to
happen. To illustrate these challenges, consider the interaction of a static
analysis tool with a dynamic language. A program analyzer computes an
over-approximation of the set of possible behaviors exhibited by the program
under study, a reflective facility must be represented by all behaviors that can
be expressed in the target language. \ie any legal sequence of instructions can
replace \eval. As dynamic languages are permissive, the tool must assume that
all functions in scope were redefined, \eg that \texttt{`+`} now opens a network
connection. A single occurrence of \eval causes the static analyzer to lose all
information about the program state and meaning of identifiers. This loss of
precision can sometimes be mitigated by analyzing the string
argument~\cite{moller03}, but if the string comes from outside the program, not
much can be done. A frustrated group of researchers argued giving up on
soundness and, instead, under-approximating dynamic features
(soundiness)~\cite{soundy}. In their words, ``a practical analysis, may pretend
that \eval does nothing unless it can precisely resolve its string argument at
compile time.'' Alas, assuming that \eval does not have side-effects or that
side-effects will not affect results is unduly optimistic.

\paragraph{Is Past Prologue?} Previous work investigated
\eval in web programming, specifically JavaScript web pages~\cite{pldi10a}. In
2011, 82\% of the 10,000 most accessed sites used \eval~\cite{ecoop11}. Yet, the
strings passed to \eval, and their behaviors, when executed, were far from
random; it was shown that when one could observe several calls, the ``shape'' of
future calls could be predicted with 97\% accuracy~\cite{oopsla12b}. Overall,
practical usage suggested that most reflective calls were relatively harmless.
While this backed up the soundiness squad's approach, does it generalize to
other application domains and to other languages?

\paragraph{The Here and Now.} In this study, we investigate the
usage of \eval in programs written in the R language. R is a language designed
by statisticians for applications in data science~\cite{r,R96}. What makes
looking at R after JavaScript interesting is that, while both languages are
dynamic, they are quite different. While one can program in an object-oriented
style in R like in JavaScript, R is mostly a lazy functional language.
JavaScript was designed to run untrusted code in a browser, while R is used for
statistical computing on desktops. JavaScript is a general-purpose language used
by a vast community of programmers, while R is used for scientific computing by
data scientists and domain experts with, often, limited programming experience.
One can distinguish between library implementers who have programming experience
and a working knowledge of R, and end-users who are typically not expert
programmers with a cursory knowledge of the language.\footnote{We surveyed
end-users and did not find a single one aware that R is lazy.} Our goal is to
highlight the differences in usage between JavaScript and R and explain them in
terms of language features, application domain and programmer experience.
Hopefully, some of our observations generalize to other languages. Our data
and code are open source and publicly available:
\url{https://github.com/PRL-PRG/evalr-experiment}.

\paragraph{The What and How.} One benefit of
R is that every package in the CRAN repository comes with examples of typical
usage. This gives us a codebase that we can analyze dynamically. To observe
\eval, we built a two-level monitoring infrastructure: we monitor programs by
instrumentation and we also monitor the inner workings of the interpreter.
Dynamic analysis is limited as it can only observe behaviors triggered by the
particular inputs passed to a program. Luckily, R libraries come with many tests
and use-cases. Our corpus is constructed to reflect the levels of sophistication
of the R community. We distinguish between \emph{CRAN packages} (\CranPackages
curated packages that pass quality checks and have tests and sample data) and
\emph{Kaggle scripts} (\KaggleUnique end-user written programs) It is reasonable
to expect \eval usage to differ between these datasets, libraries are part of a
lively and growing ecosystem, while end-user code is often thrown together, run
once, and never revisited.

\paragraph{Why do we Eval?} The results of our study suggest
that \eval is widely used for the implementation of the language, and in many
libraries. End-user code makes less frequent and less sophisticated use of
\eval. In many ways, \eval in R is as bad as it gets: it's varied, performs
side-effects and reaches to many environments. By large, the motivations for
\eval relate to various forms of language extensions and meta-programming. \Eval
is used where other languages would provide macros. But, the expressive power of
\eval is higher as it can reach arbitrarily far back in the call stack.

\section{Background and Previous work}

@@

\citet{ecoop12} gives a programming language-centric overview of the R language.
They characterized it as a lazy, vectorized, functional language with a rich
complement of dynamic features expressive enough to layer several object systems
on top of the core language. Most data types are sequences of primitive values.
For instance, \c{c("Ha","bye")} evaluates to a vector of two strings. Constants
such as \c{42} are vectors of length one. To enable equational reasoning, values
accessible through multiple aliases are copied when written to. Furthermore,
values can be tagged by attributes; these are key-value pairs. For instance, the
attribute \c{dim}-\c{c(2,2)} can be attached to the value at \c{x} by
\c{attr(x,"dim")$\leftarrow$c(2,2)}. Adding this attribute turns \c x into a
matrix. The \c{class} attribute gives a value a 'class' in the object-oriented
sense. So, \c{class(x)<-"human"} sets the class of \c{x} to \c{human}; classes
are used for method dispatch. Every linguistic construct is desugared to a
function call, even control flow statements, assignments and bracketing. All
functions can be shadowed and redefined, making R at the same time remarkably
flexible and exceedingly challenging to compile as vividly detailed
by~\citet{dls19}. R uses a relaxed call-by-need convention for passing arguments
to functions. Each argument is a thunk composed of an expression, its
environment, and a slot for the result; these are called \emph{promises}. To get
the value of an argument, the corresponding promise must be forced. Once forced,
the promise's result is cached for future use.

@@

While a data-to-code facility is available in many languages, some design
choices affect its expressive power. The key choices are the input format, the
environment in which generated code evaluates and the reflective operations
available to that code. Fig.~\ref{comp} summarizes a few designs.

@@

The input to \eval can be in any format convertible to code. JavaScript allows
arbitrary strings, Julia and R are more restrictive as they require expressions
(or abstract syntax trees). Finally, Java is the most restrictive as its
classloader only accepts complete classes in bytecode format. These differences
mostly affect users who seem more comfortable crafting strings.

The choice of the environment of \eval is essential as it determines how much of
a program \eval can observe as well as the reach of potential side-effects
performed by its execution. The most restrictive semantics is that of Java,
where newly loaded code evaluates in the environment consisting of the classes
visible from the current classloader. Julia limits \eval to the symbols visible
in global environment, so does JavaScript's strict mode. Finally, R is the most
flexible as any accessible environment can be selected and passed to \eval. The
choice of the environment is fully under the programmer's control.

The last degree of freedom is the expressive power of the code executed by
\eval. The main difference between languages lies in how much of the state of a
program is accessible through reflective operations. Julia, Java and, JavaScript
allow some form of introspection on the data that is visible in the environment
in which \eval executes. R is more flexible as lets \eval inspect the program's
call stack as well as the code of any function. Thus, any environment and any
binding in contains can be inspected and modified.

@@

The \eval function in R takes three parameters: an \c{expression} to evaluate
(\c{e}), an environment where to evaluate (\c{envir}), and an enclosure
(\c{encl}) that is used to look up objects not found in \c{envir}.\footnote{Next
to the \eval function R offers three other variants:
  \begin{inparaenum}[1.]
    \item \c{evalq} automatically quotes passed expression---a shorthand to
      \c{eval(quote(...))},
    \item \c{eval.parent(e, n)} specifies the evaluating environment in terms of
      number of call frames (\c{n}) to go back---a shorthand to \c{eval(e,
        parent.frame(n))}, and
    \item \c{local} evaluates \c{e} in a fresh environment---a shorthand to
      \c{evalq(e, new.env())}.
  \end{inparaenum} }

\begin{lstlisting}
 eval <- function(e, envir = parent.frame(),
                   encl = if(is.list(envir)) parent.frame() else baseenv()) ...
\end{lstlisting}

\noindent The expression passed to \eval can be thought of as an abstract syntax
tree. It can be parsed from a string, created manually or using reflection.

\begin{figure}[htb]
\begin{minipage}{.49\textwidth}
\begin{lstlisting}[caption={Examples of calls producing expression \c{a+b}}]
  parse(text="a+b")
  quote(a+b)
  call("+", quote(a), quote(b))

@@

\noindent The call to \c{substitute(x)} extracts the unevaluated expression from
the promise \c{x}. The function \c{match.call} returns an expression
representing the current call.

@@

\citet{ecoop11} provided the first study at scale of the behavior of \eval in
JavaScript. A corpus of 10,000 popular websites was analyzed with an
instrumented web browser to gather execution traces. Of those sites, 82\% used
\eval for purposes such as on-demand code loading, deserialization of JSON data,
or lightweight meta-programming to customize web pages. While many uses were
legitimate, just as many were unnecessary and could be replaced with equivalent
and safer code. The authors categorized inputs to \eval. For inputs in
which all named variables refer to the global scope, many patterns could be
replaced by more disciplined code~\cite{oopsla12b, moller12}. The work did not
measure code coverage, so the numbers presented are a lower bound on possible
behaviors. Furthermore, JavaScript usage in 2011 is likely different from today,
\eg Node.js was not covered. More details about dynamic analysis of JavaScript
can be found in~\cite{liang}.

@@

\noindent The pipeline runs in parallel~\cite{GNUparallel} orchestrated by a
Makefile. Servers have identical environments thanks to a docker image with all
dependencies installed.

@@

\begin{wrapfigure}{4}{5.8cm}  \small  \vspace*{-2mm}\centering
  \begin{tabular}{|r@{\,}r@{\,}l@{\,}r|r@{\,}r@{\,}l@{}r|} \hline
\multicolumn{3}{|c}{\#calls} & \#sites &
\multicolumn{3}{c}{\#calls} & \#sites \\\hline
\tt 0 &--& \tt 50    & \packageRunbina & \tt 501 &--& \tt 1000   & \packageRunbine\\
\tt 51 &--& \tt 100  & \packageRunbinb & \tt 1001 &--& \tt 1500  & \packageRunbinf\\
\tt 101 &--& \tt 250 & \packageRunbinc & \tt 1501 &--& \tt 2000  & \packageRunbing\\
\tt 251 &--& \tt 500 & \packageRunbind & \tt 2001 &--& \tt 3000 & \packageRunbinh\\\hline
\end{tabular}

@@

\medskip\noindent\EE{$min(e)=\c{V}$} Expressions that represent values are
frequently passed to \eval -- they occur in 17\% of sites. The majority of
those, \packageValOneNodePercent, are inline constants (integer or double
vectors). The rest trivially evaluate to a value, \eg~\c{1+1}.\footnote{True as
long as base functions such as \c{+} are not redefined. They typically are not,
but this is a limitation of this categorization.} In our corpus,
\packageNbCallSitesUniqueActualValue call sites only ever see a simple value,
such as:
\begin{lstlisting}
 f1 <- eval(paste("A~",paste(paste(names(X[,-1])),collapse="+")))
\end{lstlisting}
where the argument to \eval is a string which \eval simply returns. Of twenty
randomly selected \evals, XXXXX
%% UNFINED TODO \packageUsefulValueEvalPercent
of them need \eval for
some inputs. Either we are dealing with a value that needs to be constructed
dynamically, or the value is a default case that sometimes is replaced by a more
interesting expression. This form is usually evaluated in few interpreter steps;
in fact, the median is only \packageMinimizedmedianoperationscRnd. The
environment in which they evaluate is mostly irrelevant.

@@

Table~\ref{tab:provenance} summarizes the expression provenance in our corpus.
This data is obtained by dynamically tainting values as they are produced by the
various sources. Due to technical reasons, there is some imprecision in the
results. In particular, we are not able to classify all sites. Manual inspection
of numerous examples suggests that errors are rare.
